Aa Language Reference Manual

### 2016-04-11 v2/Ahir-asm/devel/docs/AaLRM.tex
Started writing system partitioner to produce hw/sw  groups from common hsys description.
Updated a bit

The downstream tools will always attempt to pipeline the do-while loop by
starting the next iteration while the current one is still in progress.
Dependency analysis on values in the loop-body is used to determine the
extent of loop pipelining.  While doing the pipelining, one can specify
two parameters as follows
\begin{verbatim}
  $dopipeline $depth 8 $buffering 2
    ...
  $while ....
\end{verbatim}
This specifies that up to 8 iterations of the loops will be kept alive
in hardware, and the amount of buffering per operation will be kept to
2.

Additionally, it is possible to specify that the loop-pipelining
be done to its extreme possibility, that is, to the maximum possible
rate that can be achieved.
\begin{verbatim}
  $dopipeline $depth 8 $buffering 2
  $fullrate // specify that extreme pipelining 
	    // should be attempted.
    ...
  $while ....
\end{verbatim}

@@

\section{Scoping Rules} \label{sec:Scopes}

@@

@@

>>>>

The downstream tools will always attempt to pipeline the do-while loop by
starting the next iteration while the current one is still in progress.
Dependency analysis on values in the loop-body is used to determine the
extent of loop pipelining.  While doing the pipelining, one can specify
two parameters as follows
\begin{verbatim}
  $dopipeline $depth 8 $buffering 2
    ...
  $while ....
\end{verbatim}
This specifies that up to 8 iterations of the loops will be kept alive
in hardware, and the amount of buffering per operation will be kept to
at least 2 (or any specified integer).  Further the buffering specification implies that at most
2 versions of the same operations will be kept in flight across multiple
loop iterations.

Additionally, it is possible to specify that the loop-pipelining
be done to its extreme possibility, that is, to the maximum possible
rate that can be achieved.
\begin{verbatim}
  $dopipeline $depth 8 $buffering 2
  $fullrate // specify that extreme pipelining 
	    // should be attempted.
    ...
  $while ....
\end{verbatim}
When the full-rate is specified, the generated circuit will
be aggressively implemented to obtain a 1-cycle loop initiation
latency.  This may lead to long combinational paths, which can
be controlled by using double buffering.

@@

\section{Scoping Rules (Deprecated!) } \label{sec:Scopes}

@@

Pipeline modules can have several parameters as follows:
\begin{verbatim}
$pipeline ($depth <integer>)? ($buffering <integer>)? ($fullrate)?
        $module [foo] $in (...) $out (...) $is
\end{verbatim}
The pipeline parameters are similar to the {\bf \$dopipeline} 
construct.

@@

An operator module is not allowed to access pipes from within.
Inside an operator module, function calls can be made only
to operator/volatile modules.
